---
title: "Level and Trend Change Summary"
date: "Compiled at `r Sys.time()`"
output: html_document
params:
  old_data_name: "Old Data"
  new_data_name: "New Data"
  old_data: !r data("old_data", package = "DiagnosticReportR"); old_data
  new_data: !r data("new_data", package = "DiagnosticReportR"); new_data
  level_threshold: 20
  trend_bins: 1
  comparison_var: "outcome"
  id_vars: !r c("year", "group")
  group_vars: "group"
  trend_var: "year"
  scatter_color_var: !r NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(DiagnosticReportR)
library(data.table)
library(ggplot2)
```

## Overview

This diagnostic report presents a basic overview of the trend and level changes 
between the data sets **`r params$old_data_name`** and 
**`r params$new_data_name`**.

## Input Data Summary

### `r params$old_data_name`

**Shape:** (`r dim(params$old_data)`)

```{r}
knitr::kable(
  head(params$old_data, n = 10),
  caption = "Head of data"
)
```

### `r params$new_data_name`

**Shape:** (`r dim(params$new_data)`)

```{r}
knitr::kable(
  head(params$new_data, n = 10),
  caption = "Head of data"
)
```


</br>

## Rank Change Analysis

**Rank Change parameters:**

 - ID variables: **`r params$id_vars`**
 - Group variables: **`r params$group_vars`**
 - Comparison variable: **`r params$comparison_var`**
 - Level threshold variable: **`r params$level_threshold`**
 - Trend bins variable: **`r params$trend_bins`**
 - Trend variable: **`r params$trend_var`**


### Level Changes

```{r}
level_changes <- rank_level(
  params$new_data,
  params$old_data,
  threshold = params$level_threshold,
  comparison_var = params$comparison_var,
  id_vars = params$id_vars,
  group_vars = params$group_vars
)

knitr::kable(
  level_changes[rank <= 10],
  caption = "Top 10 greatest changes by level"
)

```


### Trend Changes

```{r}
trend_changes <- rank_trend(
  params$new_data,
  params$old_data,
  numb_bins = as.integer(params$trend_bins),
  comparison_var = params$comparison_var,
  id_vars = params$id_vars,
  group_vars = params$group_vars,
  trend_var = params$trend_var
)

knitr::kable(
  trend_changes[rank <= 10],
  caption = "Top 10 greatest changes by trend"
)
```


</br>

## Summary Diagnostic Plots

```{r, fig.align='center', dpi=250}
level_scatter <- plot_scatter(
  data = level_changes, 
  x_var = "old_outcome", 
  y_var = "new_outcome",
  color_pt = params$scatter_color_var
)

level_scatter +
  labs(
    title = "Level Scatter",
    x = paste("Old", params$comparison_var),
    y = paste("New", params$comparison_var)
  )
```

```{r, fig.align='center', dpi=250}
trend_plot <- plot_trends(
  trend_changes, 
  time_var = params$trend_var, 
  y1_var = "old_outcome", 
  y2_var = "new_outcome", 
  colors = c("blue", "red")
)

trend_plot + labs(title = "Trend Changes")
```
